FictionEro2 - Determinants of Reality Beliefs

### 2025-06-11 study2/analysis/2_emotion.qmd
minor

---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

```{r Arousal1}
arousal <- df |> 
  ggplot(aes(x=Arousal, fill = Gender)) +
  geom_bar() +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(
    breaks = c(0, 1),
    labels = c("Not at all","Very much")) +
  labs(title = "Arousal", ) +
  facet_wrap(Gender~SexualOrientation) +
   scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal Plot}
estimate_relation(m_a) |> 
  ggplot(aes(x=SexualOrientation, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  facet_wrap(~Gender) +
  theme_abyss()
```

@@

```{r Enticement1}
enticiment <- df |> 
  ggplot(aes(x=Enticing, fill = Gender)) +
  geom_bar() +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(
    breaks = c(0, 1),
    labels = c("Not at all","Very much")) +
  labs(title = "Enticement", ) +
  facet_wrap(Gender~SexualOrientation) +
  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Valence1}
valence <- df |> 
  ggplot(aes(x=Valence, fill = Gender)) +
  geom_bar() +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(
    breaks = c(0, 1),
    labels = c("Unplesant","Pleasant")) +
  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
  labs(title = "Valence", ) +
    facet_wrap(Gender~SexualOrientation) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some images differ by whether the images were preceeded by 'photograph' or by 'AI-generated'. A possible explanation might be due to the lower number of participants compared to study1.

>>>>

---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: inline
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

```{r Arousal1}
#| fig-width: 12
arousal <- df |> 
  ggplot(aes(x=Arousal, fill = Gender)) +
  geom_bar() +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(
    breaks = c(0, 1),
    labels = c("Not at all","Very much")) +
  labs(title = "Arousal", ) +
  facet_wrap(Gender~SexualOrientation) +
   scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal Plot}
estimate_relation(m_a) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  facet_wrap(~SexualOrientation) +
  theme_abyss()
```

@@

```{r Enticement1}
#| fig-width: 12
enticiment <- df |> 
  ggplot(aes(x=Enticing, fill = Gender)) +
  geom_bar() +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(
    breaks = c(0, 1),
    labels = c("Not at all","Very much")) +
  labs(title = "Enticement", ) +
  facet_wrap(Gender~SexualOrientation) +
  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Valence1}
#| fig-width: 12

valence <- df |> 
  ggplot(aes(x=Valence, fill = Gender)) +
  geom_bar() +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(
    breaks = c(0, 1),
    labels = c("Unplesant","Pleasant")) +
  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
  labs(title = "Valence", ) +
    facet_wrap(Gender~SexualOrientation) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

Similar to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some "AI-generated" are lower then when they are presented as real photos.

### 2025-06-11 study2/analysis/3_realness.qmd
minor

p_a <- plot(cor_test(df, "Arousal", "Realness")) +
  ggplot2::facet_wrap(~Gender) +
  ggplot2::theme_bw()

p_e <- plot(cor_test(df, "Enticing", "Realness")) +
  ggplot2::facet_wrap(~Gender) +
  ggplot2::theme_bw()

p_v <- plot(cor_test(df, "Valence", "Realness")) +
  ggplot2::facet_wrap(~Gender) +
  ggplot2::theme_bw()

p_sub <- p_a/ p_e/ p_v

>>>>

p_a <- ggplot(df, aes(x = Arousal, y = Realness, color = Condition, fill = Condition)) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_wrap(~Gender) +
  scale_color_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
  scale_fill_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
  smplot2::sm_statCorr() +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 8),
    strip.placement = "outside",
    strip.background.x = element_rect(fill = "lightgrey", color = NA),
    strip.text.x = element_text(size = 10),
    strip.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 9, color = "black"),
    legend.text = element_text(size = 10)) +
   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "Arousal")

p_e <- ggplot(df, aes(x = Enticing, y = Realness, color = Condition, fill = Condition)) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_wrap(~Gender) +
  scale_color_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
  scale_fill_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
  smplot2::sm_statCorr() +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 8),
    strip.placement = "outside",
    axis.title.y = element_blank(),
    strip.background.x = element_rect(fill = "lightgrey", color = NA),
    strip.text.x = element_text(size = 10),
    axis.text.x = element_text(size = 9, color = "black"),
    legend.text = element_text(size = 10)) +
   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "Enticement")

p_v <- ggplot(df, aes(x = Valence, y = Realness, color = Condition, fill = Condition)) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_wrap(~Gender) +
  scale_color_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
  scale_fill_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
  smplot2::sm_statCorr() +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 8),
    strip.placement = "outside",
    axis.title.y = element_blank(),
    strip.background.x = element_rect(fill = "lightgrey", color = NA),
    strip.text.x = element_text(size = 10),
    axis.text.x = element_text(size = 9, color = "black"),
    legend.text = element_text(size = 10)) +
   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "Valence")

p_sub <- (p_a + theme(legend.position = "none"))| (p_e + theme(legend.position = "none"))| p_v + plot_layout(guides = "collect")
